### 2008-09-24 Latex/H2Preview/H2Prev2norm.tex
First set of changes: major changes to simple example conclusions. Also mods to feedforward...

The results of the previous section can be adapted for the case where $W_r=I$.

We note again that:
% 
\begin{equation}
\nrm{T_{\tiny{\ma{r\\w}}\rightarrow z}}^2_2 =
\nrm{T_{w\rightarrow z}}^2_2+
\nrm{T_{r\rightarrow z}}^2_2. \label{proj_prop}
\end{equation}
%
As observed in Corollary~\ref{cor:minwandr}, the optimal preview controller minimises $\nrm{T_{w\rightarrow z}}_2$. Since $X_{gg}$ and $Y_g$ are the solutions to the DAREs associated with the problem of minimising $\nrm{T_{w\rightarrow z}}_2$, we may use the results in Sections \ref{subsec:stdH2FI} and \ref{subsec:stdH2OF} to write:
\als{
\gamma_{wc}^2&=\textrm{Tr}\left\{(D_{11gw}+D_{12}F_{0w})'(D_{11gw}+D_{12}F_{0w})\right.\\ &\left.\qquad+(B_{1gw}+B_{2g}F_{0w})'X_{gg}(B_{1gw}+B_{2g}F_{0w})\right\}\\
\gamma_{wf}^2&=\textrm{Tr}\left\{\bar R\left( (L_{0y}D_{21gw}-F_{0w})(L_{0y}D_{21gw}-F_{0w})'\right.\right.\\ &\left.\left.\qquad+(L_{0y}C_{2g}-F_{2g})Y_{gg}(L_{0y}C_{2g}-F_{2g})'\right) \right\}\\
\nrm{T_{w\rightarrow z}}^2_2&=\gamma_{wc}^2+\gamma_{wf}^2,
} 
which are independent of the preview length.

We now turn our attention to the evaluation of $\nrm{T_{r\rightarrow z}}_2$. Since the signal $r$ is `known' to the controller, it does not introduce an estimation error. As a result the output feedback controller achieves exactly the same transfer function $T_{r\rightarrow z}$ as the full-information controller, $K_{FI}$. Thus:
\als{
T_{r\rightarrow z}=\ssmodf{A+B_2F_2}{\ma{B_{2g}F_{0r}\\B_p}}{C_1+D_{12}F_2}{D_{12}F_{0r}}.
}
%
Note that $X$ satisfies: 
\als{(A+B_2F_2)'X(A+B_2F_2)+(C_1+D_{12}F_2)'(C_1+D_{12}F_2),}
and so using equation (\ref{eqn:2normcomp}) we may write:
\als{
\nrm{T_{r\rightarrow z}}^2_2 &=\tra{\left(D_{12}F_{0r}\right)'D_{12}F_{0r}+\ma{B_{2g}F_{0r}\\B_p}'\ma{X_{gg}&X_{gp}\\X_{gp}'&X_{pp}}\ma{B_{2g}F_{0r}\\B_p}}.
} 
\mbox{where $F_{0r}=-{\bar R}^{-1}B_{2g}'X_{gp}B_p$. The above expression may be simplified to} 
\aln{
\nrm{T_{r\rightarrow z}}^2_2&=\tra{B_p'X_{pp}B_p-F_{0r}'\bar RF_{0r}\label{eqn:gamrmedeff}}.
}
%
Our next task is to find an efficient method for computing $B_p'X_{pp}B_p$. Using the $W_r=I$ version of (\ref{eqn:Xdd}), we can write:
\als{
X_{pp}&=A_p'X_{pp}A_p+\hat Q-F_{2p}'\bar{R}F_{2p}\\
\mbox{in which} \\
\hat Q &= C_{p}'B_{1gr}'X_{gg}B_{1gr}C_{p}+A_p'X_{gp}'B_{1gr}C_{p}+C_{p}'B_{1gr}'X_{gp}A_p+C_{p}'D_{11gr}'D_{11gr}C_{p}.
}

Substituting this into itself leads to:

\als{
X_{pp}=\sum^{N-1}_{j=0}{A_p^j}'(\hat Q - F_{2p}'\bar{R}F_{2p})A_p^j.
}
%
Note that post-multiplying by $A_p^kB_p$ has the effect of selecting individual block columns of the preceding matrix, that $C_pA_p^kB_p=0 \,\, \forall k \neq N-1$, and that $A_p^N=0$. This means that:
%
\[
B_p'X_{pp}B_p=B_{1gr}'X_{gg}B_{1gr}+D_{11gr}'D_{11gr}-F_{2p0}'\bar{R}F_{2p0} - \sum_{j=0}^{N-2}S' A^j_{cg} B_{2g} {\bar R}^{-1} B_{2g}' {A^j_{cg}}' S,
\]
where $F_{2p0}$ is the left-most block column of $F_{2p}$ and is given by:
\begin{equation}
F_{2p0}=-\bar R^{-1}\left(B_{2g}'X_{gg}B_{1gr}+D_{12}'D_{11gr}\right). \label{eqn:F2p0}
\end{equation}
%
Combining this with (\ref{eqn:gamrmedeff}), and using (\ref{eqn:Xgp}), leads to 
\als{
\nrm{T_{r\rightarrow z}}^2_2=\tra{\underbrace{B_{1gr}'X_{gg}B_{1gr}+D_{11gr}'D_{11gr}-F_{2p0}'\bar{R}F_{2p0}}_{\mbox{No preview}}-\underbrace{\sum_{j=0}^{N-1}S' A^j_{cg} B_{2g}{\bar R}^{-1} B_{2g}'{A^j_{cg}}'S}_{\mbox{Preview reduction}}}.
}
In order to judge how much preview to use, we need to know the value of the maximum possible improvement due to preview action. Suppose the matrix $\Gamma$ satisfies:
\als{
\Gamma=A_{cg}\Gamma A_{cg}'+B_{2g}\bar R^{-1}B_{2g}'
,}
which implies that:
\als{
\Gamma=\sum_{j=0}^{\infty}A_{cg}^jB_{2g}\bar R ^{-1}B_{2g}'{A_{cg}'}^{j}
.}
Thus the reduction in $\nrm{T_{r\rightarrow z}}_2^2$ due to preview is bounded above by 
\[
\tra{S'\Gamma S},
\]
and evaluating this limit only requires the solution of an $n_g$-dimensional Lyapunov equation.
This provides a useful bound on the achievable norm reduction one might obtain using preview. For example, one could continue adding preview points, until 95\%  of the maximum possible benefit had been achieved.

>>>>

It is easy to check that the results of the previous sections carry over for $W_r=I$. All that is required is to remove the  gains associated with the states of $W_r$.

We note again that:
% 
\begin{equation}
\nrm{T_{{[r'\,\,w']'}\rightarrow z}}^2_2 =
\nrm{T_{w\rightarrow z}}^2_2+
\nrm{T_{r\rightarrow z}}^2_2. \label{proj_prop}
\end{equation}
%
As observed in Corollary~\ref{cor:minwandr}, the optimal preview controller minimises $\nrm{T_{w\rightarrow z}}_2$. Since $X_{gg}$ and $Y_g$ are the solutions to the DAREs associated with the problem of minimising $\nrm{T_{w\rightarrow z}}_2$, we may use the results in Sections \ref{subsec:stdH2FI} and \ref{subsec:stdH2OF} to write:
\als{
\gamma_{wc}^2&=\textrm{Tr}\left\{(D_{11gw}+D_{12}F_{0w})'(D_{11gw}+D_{12}F_{0w})\right.\\ &\left.\qquad+(B_{1gw}+B_{2g}F_{0w})'X_{gg}(B_{1gw}+B_{2g}F_{0w})\right\}\\
\gamma_{wf}^2&=\textrm{Tr}\left\{\bar R\left( (L_{0y}D_{21gw}-F_{0w})(L_{0y}D_{21gw}-F_{0w})'\right.\right.\\ &\left.\left.\qquad+(L_{0y}C_{2g}-F_{2g})Y_{gg}(L_{0y}C_{2g}-F_{2g})'\right) \right\}\\
\nrm{T_{w\rightarrow z}}^2_2&=\gamma_{wc}^2+\gamma_{wf}^2,
} 
which are independent of the preview length.

We now turn our attention to the evaluation of $\nrm{T_{r\rightarrow z}}_2$. Since the signal $r$ is `known' to the controller, it does not introduce an estimation error. As a result the output feedback controller achieves exactly the same transfer function $T_{r\rightarrow z}$ as the full-information controller, $K_{FI}$. Thus:
\als{
T_{r\rightarrow z}=\ssmodf{A+B_2F_2}{\ma{B_{2g}F_{0r}\\B_p}}{C_1+D_{12}F_2}{D_{12}F_{0r}}.
}
%
Note that $X$ satisfies: 
\als{(A+B_2F_2)'X(A+B_2F_2)+(C_1+D_{12}F_2)'(C_1+D_{12}F_2),}
and so using equation (\ref{eqn:2normcomp}) we may write:
\als{
\nrm{T_{r\rightarrow z}}^2_2 &=\tra{\left(D_{12}F_{0r}\right)'D_{12}F_{0r}+\ma{B_{2g}F_{0r}\\B_p}'\ma{X_{gg}&X_{gp}\\X_{gp}'&X_{pp}}\ma{B_{2g}F_{0r}\\B_p}}.
} 
\mbox{where $F_{0r}=-{\bar R}^{-1}B_{2g}'X_{gp}B_p$. The above expression may be simplified to} 
\aln{
\nrm{T_{r\rightarrow z}}^2_2&=\tra{B_p'X_{pp}B_p-F_{0r}'\bar RF_{0r}\label{eqn:gamrmedeff}}.
}
%
Our next task is to find an efficient method for computing $B_p'X_{pp}B_p$. Using the $W_r=I$ version of (\ref{eqn:Xdd}), we can write:
\als{
X_{pp}&=A_p'X_{pp}A_p+\hat Q-F_{2p}'\bar{R}F_{2p}}
in which
\als{
\hat Q &= C_{p}'B_{1gr}'X_{gg}B_{1gr}C_{p}+A_p'X_{gp}'B_{1gr}C_{p}+C_{p}'B_{1gr}'X_{gp}A_p+C_{p}'D_{11gr}'D_{11gr}C_{p}.
}
Substituting this into itself leads to:
\als{
X_{pp}=\sum^{N-1}_{j=0}{A_p^j}'(\hat Q - F_{2p}'\bar{R}F_{2p})A_p^j.
}
%
Note that post-multiplying by $A_p^kB_p$ has the effect of selecting individual block columns of the preceding matrix, that $C_pA_p^kB_p=0 \,\, \forall k \neq N-1$, and that $A_p^N=0$. This means that:
%
\[
B_p'X_{pp}B_p=B_{1gr}'X_{gg}B_{1gr}+D_{11gr}'D_{11gr}-F_{2p0}'\bar{R}F_{2p0} - \sum_{j=0}^{N-2}S' A^j_{cg} B_{2g} {\bar R}^{-1} B_{2g}' {A^j_{cg}}' S,
\]
where $F_{2p0}$ is the left-most block column of $F_{2p}$ and is given by:
\begin{equation}
F_{2p0}=-\bar R^{-1}\left(B_{2g}'X_{gg}B_{1gr}+D_{12}'D_{11gr}\right). \label{eqn:F2p0}
\end{equation}
%
Combining this with (\ref{eqn:gamrmedeff}), and using (\ref{eqn:Xgp}), leads to 
\aln{
\nrm{T_{r\rightarrow z}}^2_2=\tra{\underbrace{B_{1gr}'X_{gg}B_{1gr}+D_{11gr}'D_{11gr}-F_{2p0}'\bar{R}F_{2p0}}_{\mbox{Zero preview}}-\underbrace{\sum_{j=0}^{N-1}S' A^j_{cg} B_{2g}{\bar R}^{-1} B_{2g}'{A^j_{cg}}'S}_{\mbox{Preview reduction}}}.
\label{eqn:H2CostSplit}}
In order to judge how much preview to use, we need to know the value of the maximum possible improvement due to preview action. Suppose the matrix $\Gamma$ satisfies:
\als{
\Gamma=A_{cg}\Gamma A_{cg}'+B_{2g}\bar R^{-1}B_{2g}'
,}
which implies that:
\als{
\Gamma=\sum_{j=0}^{\infty}A_{cg}^jB_{2g}\bar R ^{-1}B_{2g}'{A_{cg}'}^{j}
.}
Comparing this to (\ref{eqn:H2CostSplit}), it follows that the maximum reduction in $\nrm{T_{r\rightarrow z}}_2^2$ due to preview is given by: 
\[
\tra{S'\Gamma S},
\]
and evaluating this limit only requires the solution of an $n_g$-dimensional Lyapunov equation (in addition to the $n_g$ dimensional DARE required to evaluate $S$). The following quantity provides a useful measure of the fraction of the maximum norm reduction that has been achieved:
\aln{\gamma_{\,_{\%,imp}}=100\times \tra{S'\Gamma S}^{-1}{\left(\sum_{j=0}^{N-1}S' A^j_{cg} B_{2g}{\bar R}^{-1} B_{2g}'{A^j_{cg}}'S\right)}.\label{eqn:gamimp}} 
%This provides a useful bound on the achievable norm reduction one might obtain using preview. 
This can be used to determine how much preview to use; for example, one might continue adding preview points until $\gamma_{\,_{\%,imp}} >99\%$.

### 2008-09-24 Latex/H2Preview/H2PrevIntro.tex

One of the first papers to recognise the importance of preview control is \cite{Sheridan}; three preview control models are described. In the third of these models open-loop optimal preview controls are found using dynamic programming. The earliest applied work on preview control dates back to \cite{Bender_1968_PrevSusp}, where Wiener filter theory was used to design an active suspension with road preview. Bender's solution required the transfer function from the previewed path to the vehicle's acceleration to be unstable --- such a solution is not implementable. Much of the subsequent work on preview tracking has its origins in the 1973 PhD thesis of M. Tomizuka~\cite{Tomi_1973_Thesis}, in which  the preview control task is cast in a discrete-time linear quadratic regulator framework by augmenting the plant dynamics with a delay line model. In this formulation the number of states grows in direct proportion to the preview length and so a direct solution of the corresponding Riccati equations becomes computationally infeasible for long preview lengths. Tomizuka presented an efficient recursive method for solving these large equations. A continuous-time version of a LQ preview control problem is studied in \cite{Tomizuka_1975_ContinuousLQPreview}, while a continuous-time preview control problem is given a stochastic interpretation in \cite{Lindquist}.

@@

Figure~\ref{fig:SimpleSISOPrev} illustrates a simple example that may be used to highlight the benefit of preview, the broad structure of the controller, and the effect of preview on the achievable $\htwo$-norm of the closed-loop system. In this formulation, the preview action arises because of the delay line $\Phi$. The input to the controller is $r$, which is the future value of the reference, and $K$ is chosen so as to ensure that $e$ is `small', and hence the plant output follows $\Phi r$ as closely as possible. 
\begin{figure}
\stdcontrolfrags
\begin{center}
\includegraphics[width=0.4\hsize]{./diags/SimpleExampleNominalNoK2.eps}
\end{center}
\caption{A simple SISO open-loop preview tracking problem. The transfer function $\Phi=\z^{-N}$ is an $N$-step delay, $G$ is the plant to be controlled, and $K$ is a feedforward controller. The signal $r$ is the \textit{future} value of the reference, and $e$ is the tracking error.}
\label{fig:SimpleSISOPrev}
\end{figure}
%
First define the error system:
\als{E(\z)=G(\z)K(\z)-\Phi(\z),}
and assume that $G(\z)$ is stable; in the case that $G(\z)$ is unstable, it could be replaced by $\hat G(\z)=G(\z)(1-G(\z)K_f(\z))^{-1}$ in which $K_f(\z)$ is a stabilising feedback controller. Providing that $G(\z)$ has all its zeros inside the unit circle, perfect tracking ($E(\z)=0$) may be achieved by simply setting $K(\z)=G(\z)^{-1}\Phi(\z)$. 
However, if $G(\z)$ is {NMP}, then such a $K(\z)$ is not internally stabilising and a controller must be found that recognises the limits imposed by {NMP} zeros on the achievable tracking performance. %Such limitations are well known for non-preview systems (i.e. $N=0$ and $\Phi=1$), and are investigated in some detail in \cite{Middleteon_2004_PrevPerf} and \cite{Mirkin_2004_FixedLagPerfSaturation} for the preview case.

@@

Point 3 merits further discussion. A central tenet of this paper is that the preview length could be sufficiently large that solution of the associated {DARE} is computationally intractable. However, it might be argued that it is never necessary to use a large preview length because one could simply reduce the sampling rate until $N$ becomes sufficiently small.  In \cite{Middleteon_2004_PrevPerf}, a similar example is treated in continuous-time and it is found that the required preview \textit{time} is purely a function of the position of the continuous-time zero. The discrete-time equivalent is: for a given performance improvement, the preview time $NT_s$ (where $T_s$ represents the sample time) is determined by the position of the continuous-time zero. This fact can be seen by considering the effect of $T_s$ on the magnitude of $c_z$ in (\ref{eqn:H2normsimple}). Typically, the sampling rate is determined by the frequency at which tracking or disturbance rejection is required, and also by the frequency of any unstable poles \citep{Houpis_1991_DigitalControlSystems}. It therefore follows that a combination of low frequency zeros (which impose a large $NT_s$), and higher frequency performance specifications (which impose a low $T_s$), would lead unavoidably to a large preview length ($N$).% in order to achieve 95\% of the maximum available benefit due to preview.

>>>>

One of the first papers to recognise the importance of preview control is \cite{Sheridan}, in which three preview control models are described. In the third of these models open-loop optimal preview controls are found using dynamic programming. The earliest applied work on preview control dates back to \cite{Bender_1968_PrevSusp}, where Wiener filter theory was used to design an active suspension with road preview. This solution was not implementable as it required the transfer function from the previewed path to the vehicle's acceleration to be unstable. Much of the subsequent work on preview tracking has its origins in the 1973 PhD thesis of M. Tomizuka~\cite{Tomi_1973_Thesis}, in which  the preview control task is cast in a discrete-time linear quadratic regulator framework by augmenting the plant dynamics with a delay line model. In this formulation the number of states grows in direct proportion to the preview length and so a direct solution of the corresponding Riccati equations becomes computationally infeasible for long preview lengths. Tomizuka presented an efficient recursive method for solving these large equations. A continuous-time version of a LQ preview control problem is studied in \cite{Tomizuka_1975_ContinuousLQPreview}, while a continuous-time preview control problem is given a stochastic interpretation in \cite{Lindquist}.

@@

Figure~\ref{fig:SimpleSISOPrev} illustrates a simple example that may be used to highlight the benefit of preview, the broad structure of the controller, and the effect of preview on the achievable $\htwo$-norm of the closed-loop system. In this formulation, the preview action arises because of the delay line $\Phi$. The input to the controller is $r$, which is the future value of the reference, and $K$ is chosen so as to ensure that $e$ is `small', and hence the plant output follows $\Phi r$ as closely as possible. 
\begin{figure}
\stdcontrolfrags
\begin{center}
\includegraphics[width=0.4\hsize]{./diags/SimpleExampleNominalNoK2.eps}
\end{center}
\caption{A simple SISO open-loop preview tracking problem. The transfer function $\Phi=\z^{-N}$ is an $N$-step delay, $G$ is the plant to be controlled, and $K$ is a feedforward controller. The signal $r$ is the \textit{future} value of the reference, and $e$ is the tracking error.}
\label{fig:SimpleSISOPrev}
\end{figure}
%
Now define the error system:
\als{E(\z)=G(\z)K(\z)-\Phi(\z),}
and assume that $G(\z)$ is stable; in the case that $G(\z)$ is unstable, it could be replaced by $\hat G(\z)=G(\z)(1-G(\z)K_f(\z))^{-1}$ in which $K_f(\z)$ is a stabilising feedback controller. Providing that $G(\z)$ has all its zeros inside the unit circle, perfect tracking ($E(\z)=0$) may be achieved by simply setting $K(\z)=G(\z)^{-1}\Phi(\z)$. 
However, if $G(\z)$ is {NMP}, then such a $K(\z)$ is not internally stabilising and a controller must be found that recognises the limits imposed by {NMP} zeros on the achievable tracking performance. %Such limitations are well known for non-preview systems (i.e. $N=0$ and $\Phi=1$), and are investigated in some detail in \cite{Middleteon_2004_PrevPerf} and \cite{Mirkin_2004_FixedLagPerfSaturation} for the preview case.

@@

Point 3 merits further discussion. A central tenet of this paper is that the preview length could be sufficiently large that solution of the associated {DARE} is computationally intractable. However, it might be argued that it is never necessary to use a large preview length because one could simply reduce the sampling rate until $N$ becomes sufficiently small.  In \cite{Middleteon_2004_PrevPerf}, an example similar to Figure \ref{fig:SimpleSISOPrevexample} is treated in continuous-time, and it is found that the required preview \textit{time} is purely a function of the position of the continuous-time zero. The discrete-time equivalent of this result is that: for a given performance improvement, the preview time $NT_s$ (where $T_s$ represents the sample time) is determined by the position of the \textit{continuous-time} zero. This fact can be seen by considering the effect of $T_s$ on the magnitude of $c_z$ in (\ref{eqn:H2normsimple}). Typically, the sampling rate is determined by the frequency at which tracking or disturbance rejection is required, and also by the frequency of any unstable poles \citep{Houpis_1991_DigitalControlSystems}. It therefore follows that a combination of low frequency zeros (which impose a large $NT_s$), and higher frequency performance specifications (which impose a low $T_s$), would lead unavoidably to a large preview length ($N$).% in order to achieve 95\% of the maximum available benefit due to preview.

### 2008-09-24 Latex/H2Preview/H2PrevSummary.tex

This phenomenon was first noticed in \cite{Tomizuka_1975_OptDiscretePreview}, with a proof provided in Section \ref{sec:H2FI}. It is instructive to consider the influence of $W_r$ from a stochastic perspective. Since $\eta$ is assumed to be a realisation of a white-noise process, then a dynamic $W_r$ provides statistical information on future values of $r$. If, for example, $W_r$ is low-pass, the $r(k)$'s will become correlated and hence $W_r$ will introduce `statistical preview' beyond the preview horizon. We would therefore expect $W_r$ to reduce the need for preview, and also that its influence on the control would decline as $N$ tends to infinity.

@@

\begin{description}
\item[Preview improves steady-state disturbance rejection.] 
Figure~\ref{fig:BetterSSWithIncN} illustrates the `non-responsiveness' of the closed-loop system in the case of no reference weight, and a low preview horizon. In the limiting case, where there is zero preview and no reference weighting, the controller does not have any information about the value of the reference at the next time step, and so it cannot make a decision about the direction in which to send the plant. Therefore, the tracking error cost cannot be reduced, and so the optimal controller can only minimise the control cost, leading to a choice of $u=0$.

@@

tracking-error filter. A low-pass weight on the tracking error improves the steady-state tracking performance, without needing to change the assumed frequency content of the reference signal (i.e. without changing $W_r$). Even if $W_r=1$,  the inclusion of a low-pass tracking-error filter ($W_e$) ensures that the low-frequency components of $r$ will be tracked accurately, in contrast to Figure~\ref{fig:BetterSSWithIncN}. This is accomplished via feedback based on the states of $W_e$, which is low-pass and so there is no initial `spike' in the control signal -- see Figure \ref{fig:ReducingControlWithIncreasingN}. 

@@

\item[Preview only improves low frequency tracking performance.] For a low-pass plant, high frequency tracking performance is limited by the prohibitive size of the control action, which is a fundamental feature of the plant and cannot be changed by anticipative action. This effect is illustrated in Figure~\ref{fig:sigmah2}. In this example, preview improves the low-frequency performance by reducing the magnitude of both the tracking error and the control signal. %The price for this improvement appears to be larger control action at higher frequencies

@@

\subfloat[$W_e=\frac{1}{\z-1}$]{\includegraphics[width=\columnwidth]{./diags/WeightedSigmaH2.eps}}
\caption{Bode plots of the closed-loop transfer functions $T_{r\rightarrow e}$ and $T_{r\rightarrow u}$ which result from application of the $\hinf$-optimal controls.\label{fig:sigmah2} The unweighted plant is considered in (a), and a low-pass $W_e$ is employed in (b).}
\end{figure}
\item[Integral action with output feedback.]
An output-feedback tracking controller with integral action is described by Figure \ref{fig:TrackSysIntegDesign}, which also serves to
illustrate the complexity of problems that may be tackled  using the framework in Figure 1. The integrated error signal must be included in the measurements in order to ensure that the integrator state is detectable.

Tuning the relative magnitudes of $W_{e1}$ and $W_{e2}$ is akin to adjusting the gains in a PI controller. The ability to adjust the integral gain is useful, because too much integral action can be detrimental to stability and/or the transient response. In fact a `derivative' signal could also be added, thus completing the PID analogy and facilitating tuning of the preview controller.

>>>>

This phenomenon was first noticed in \cite{Tomizuka_1975_OptDiscretePreview}, with a proof provided in Section \ref{sec:H2FI}. It is instructive to consider the influence of $W_r$ from a stochastic perspective. Since $\eta$ is assumed to be a realisation of a white-noise process, then a dynamic $W_r$ provides statistical information on future values of $r$. If, for example, $W_r$ is low-pass, the $r(k)$'s become correlated and hence $W_r$ introduces `statistical preview' beyond the preview horizon. We would therefore expect $W_r$ to reduce the need for preview, and also that its influence on the control would decline as $N$ tends to infinity.

@@

\begin{description}
\item[Preview improves steady-state tracking.] 
Figure~\ref{fig:BetterSSWithIncN} illustrates the `non-responsiveness' of the closed-loop system in the case of no reference weight, and a low preview horizon. In the limiting case, where there is zero preview and no reference weighting, the controller does not have any information about the value of the reference at the next time step, and so it cannot make a decision about the direction in which to send the plant. Therefore, the tracking error cost cannot be reduced, and so the optimal controller can only minimise the control cost, leading to a choice of $u=0$.

@@

tracking-error filter. A low-pass weight on the tracking error improves the low-frequency tracking performance, without needing to change the assumed frequency content of the reference signal (i.e. without changing $W_r$). Note that a step change in the reference does not lead to a `spike' in the control signal -- see Figure \ref{fig:ReducingControlWithIncreasingN}. 

@@

\item[Preview only improves low frequency tracking performance.] For a low-pass plant, high frequency tracking performance is limited by the prohibitive size of the control action. This is a fundamental feature of the plant and cannot be changed by anticipative action. This effect is illustrated in Figure~\ref{fig:sigmah2}, where preview improves the low-frequency performance by reducing the magnitude of both the tracking error and the control signal. %The price for this improvement appears to be larger control action at higher frequencies

@@

\subfloat[$W_e=\frac{1}{\z-1}$]{\includegraphics[width=\columnwidth]{./diags/WeightedSigmaH2.eps}}
\caption{Bode plots of the closed-loop transfer functions $T_{r\rightarrow e}$ and $T_{r\rightarrow u}$ which result from application of the $\hinf$-optimal controls.\label{fig:sigmah2} The unweighted plant is considered in (a), and a low-pass $W_e$ is employed in (b).}
\end{figure}
\item[Integral action with output feedback.]
An output-feedback tracking controller with integral action is described by Figure \ref{fig:TrackSysIntegDesign}, which also serves to
illustrate the complexity of problems that may be tackled  using the framework in Figure 1. Note that the integrated error signal must be included in the measurements in order to ensure that the integrator state is detectable.

Tuning the relative magnitudes of $W_{e1}$ and $W_{e2}$ is akin to adjusting the gains in a PI controller. %The ability to adjust the integral gain is useful, because too much integral action can be detrimental to stability and/or the transient response. 
In fact a `derivative' signal could also be added, thus completing the PID analogy and facilitating tuning of the preview controller.
